---
title: "DV_FinalProject"
output: word_document
---

**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  03 Tableau Workbooks - this is where the Tableau workbook(s) goes (twbx format)
  
  04 Shiny - contains our workflows and the code for the visualizations along with code used to create Shiny app.

***

##Explanation of Data:
Hyunji's Intro about banking data
  add sentece(s) about blended data
  
***

##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_ExtractTransform.R", echo = TRUE)
```
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_ExtractTransformJob.R", echo = TRUE)
```
```{r}
source("../01 Data/R_Load.R", echo = TRUE)
```

***

##Label Explanations:
here

***

##Non_Aggregated Measures Analysis: 

####Boxplot:
words

##Aggregrated Measures Analysis:

####Histogram:

#####Legit Title:
words

#####Legit Title No 2:
words

##Scatter Plots:

####Legit Title 1:
words

####Legit Title No 2:
words

##Crosstabs:

####Legit Title:
words

##Barcharts:

####Legit Title 1:
words

####Legit Title 2:
*Also demonstrates data blending*

words

####Legit Title 3:
words

